The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2024-11-15 borel-regularity.tex
Name ODE unknown more consistently
Tweak lemma statement

Furthermore, when $-\alpha$ is a root of $P$, the integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$ has a special solution $\psi_\alpha$ which is distinguished, up to scaling, by its power-law asymptotics at $\zeta = \alpha$~\cite[Theorem~4]{reg-sing-volterra}. This solution is regular enough to have a well-defined Laplace transform $\Psi_\alpha$, which is a special solution of $\mathcal{P}\Phi = 0$ distinguished by its own characteristic asymptotics.
\begin{theorem}[also \ref{re:thm:exist_uniq_ODE}]\label{thm:exist_uniq_ODE}
Let $-\alpha$ be a root of $P$. Consider an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and does not touch any other root of $P(-\zeta)$. The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
\[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexp{-\tau_\alpha-1}(\widehat{\Omega}_\alpha^\bullet) \right] \]
of the space $e^{-\alpha z} \dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\bullet)$ from Definition~\ref{def:H_hat}.
\end{theorem}
The special solution $\psi_\alpha$ is also regular enough to have a ``fractionally shifted'' power series expansion $\series{\psi}_\alpha$, whose formal Laplace transform $\series{\Psi}_\alpha$ is a formal solution of $\mathcal{P}\series{\Phi} = 0$. By construction, $\series{\Psi}_\alpha$ is Borel summable, with Borel sum $\Psi_\alpha$.
\begin{theorem}[also \ref{re:thm:soln_is_Borel_sum}]\label{thm:soln_is_Borel_sum}
The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is the Borel sum of a formal trans-monomial solution $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$ of the equation $\mathcal{P}\series{\Phi} = 0$.
\end{theorem}
We can use this result to show that $\Psi_\alpha$ is Borel regular. Because of the fractional power $z^{-\tau_\alpha}$, we use Lemma~\ref{lem:laplace-bridge} instead of a more standard result on the asymptotics of a Borel sum, such as Theorem~5.20 of \cite{diverg-resurg-i}.
\begin{corollary}[also \ref{re:cor:soln_borel-reg}]\label{cor:soln_borel-reg}
The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is Borel regular. This is because $\Psi_\alpha$ is asymptotic to the formal solution $\series{\Psi}_\alpha$ from Theorem~\ref{thm:soln_is_Borel_sum}.
\end{corollary}
In many cases, by choosing from among the solutions $\Psi_\alpha$, we can build a frame of Borel-regular solutions of the equation $\mathcal{P}\Phi = 0$.

@@

Choose a translation coordinate $\zeta$ on $B$. Let $\Omega_\alpha \subset B$ be an open set with the point $\zeta = \alpha$ on its boundary, and let $\Omega_\beta \subset B$ be an open set with $\zeta = \beta$ on its boundary. For any $\phi \in \singexpalg{\sigma}(\Omega_\alpha)$ and $\psi \in \singexpalg{\sigma'}(\Omega_\beta)$, the convolution product $\phi \ast_{\zeta, \alpha, \beta} \psi$ is the function on $B$ defined by the integral

@@

For any two functions $\phi \in \singexpalg{\sigma}(\Omega)$ and $\psi \in \singexpalg{\sigma'}(\Omega)$, with $\sigma, \sigma' \in (-1, \infty)$, we have

>>>>

Furthermore, when $-\alpha$ is a root of $P$, the integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$ has a special solution $\psi_\alpha$ which is distinguished, up to scaling, by its power-law asymptotics at $\zeta = \alpha$~\cite[Theorem~4]{reg-sing-volterra}. This solution is regular enough to have a well-defined Laplace transform $\Psi_\alpha$, which is a special solution of $\mathcal{P}\Phi = 0$ distinguished by its own characteristic asymptotics.
\begin{theorem}[also \ref{re:thm:exist_uniq_ODE}]\label{thm:exist_uniq_ODE}
Let $-\alpha$ be a root of $P$. Consider an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and does not touch any other root of $P(-\zeta)$. The equation $\mathcal{P}\Phi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
\[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexp{-\tau_\alpha-1}(\widehat{\Omega}_\alpha^\bullet) \right] \]
of the space $e^{-\alpha z} \dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\bullet)$ from Definition~\ref{def:H_hat}.
\end{theorem}
The special solution $\psi_\alpha$ is also regular enough to have a ``fractionally shifted'' power series expansion $\series{\psi}_\alpha$, whose formal Laplace transform $\series{\Psi}_\alpha$ is a formal solution of $\mathcal{P}\series{\Phi} = 0$. By construction, $\series{\Psi}_\alpha$ is Borel summable, with Borel sum $\Psi_\alpha$.
\begin{theorem}[also \ref{re:thm:soln_is_Borel_sum}]\label{thm:soln_is_Borel_sum}
The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is the Borel sum of a formal trans-monomial solution $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$ of the equation $\mathcal{P}\series{\Phi} = 0$.
\end{theorem}
We can use this result to show that $\Psi_\alpha$ is Borel regular. Because of the fractional power $z^{-\tau_\alpha}$, we use Lemma~\ref{lem:laplace-bridge} instead of a more standard result on the asymptotics of a Borel sum, such as Theorem~5.20 of \cite{diverg-resurg-i}.
\begin{corollary}[also \ref{re:cor:soln_borel-reg}]\label{cor:soln_borel-reg}
The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is Borel regular. This is because $\Psi_\alpha$ is asymptotic to the formal solution $\series{\Psi}_\alpha$ from Theorem~\ref{thm:soln_is_Borel_sum}.
\end{corollary}
In many cases, by choosing from among the solutions $\Psi_\alpha$, we can build a frame of Borel-regular solutions of the equation $\mathcal{P}\Phi = 0$.

@@

Choose a translation coordinate $\zeta$ on $B$. Let $\Omega_\alpha \subset B$ be an open set with the point $\zeta = \alpha$ on its boundary, and let $\Omega_\beta \subset B$ be an open set with $\zeta = \beta$ on its boundary. For any $\phi \in \singexpalg{\sigma}(\Omega_\alpha)$ and $\psi \in \singexpalg{\sigma'}(\Omega_\beta)$ with $\sigma,\sigma'\in (-1,\infty)$, the convolution product $\phi \ast_{\zeta, \alpha, \beta} \psi$ is the function on $B$ defined by the integral

@@

For any two functions $\phi \in \singexpalg{\sigma}(\Omega)$ and $\psi \in \singexpalg{\sigma'}(\Omega)$ with $\sigma, \sigma' \in (-1, \infty)$, we have
